### 2023-02-01 appendix.Rmd
revisions #3

---
output:
  pdf_document: default
  html_document: default
---
\renewcommand{\appendixname}{Supplementary Materials}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{table}} \setcounter{equation}{0}

# Supplementary Materials

@@

```{r echo=F, warning=F, message=F}
loadd(cfa1)
loadd(cfa2)
```

@@

@@

```{r samplePlot, echo=FALSE, warning=F, message=F, fig.width=10, fig.height=6, fig.cap="(ref:samplePlotCaption)"}
readd(samplePlot)
```

@@

```{r screePlot, echo=FALSE, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="(ref:screePlotCaption)"}
readd(screePlot)
```

@@

(ref:indGamesPlotSDOCaption) _Individual game decisions predicting Social Dominance Orientation in Study 1._ Lines are predictions from linear regressions, controlling for Right Wing Authoritarianism, game comprehension, and demographics. Multiple comparisons are accounted for by using a Bonferonni-corrected alpha level. Blue plots are cooperation decisions, orange plots are punishment decisions. Numbers are unstandardised coefficients. *_p_ < 0.003. DG = Dictator Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), PGG = Public Goods Game, SH = Stag Hunt Game, UG1 = Ultimatum Game (Offer), TPP1 = Third-Party Punishment Game (Steal), SPP1 = Second-Party Punishment Game (Cooperate), SHP1 = Stag Hunt Game with Punishment (Coordinate), UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP2 = Second-Party Punishment Game (Punish Cooperator), SPP3 = Second-Party Punishment Game (Punish Defector), SHP2 = Stag Hunt Game with Punishment (Punish Coordinator), SHP3 = Stag Hunt Game with Punishment (Punish Defector).

```{r indGamesPlotSDO, echo=FALSE, warning=F, message=F, fig.width=7, fig.height=4, fig.cap="(ref:indGamesPlotSDOCaption)"}
readd(indGamesPlotSDO)
```

@@

(ref:indGamesPlotRWACaption) _Individual game decisions predicting Right Wing Authoritarianism in Study 1._ Lines are predictions from linear regressions, controlling for Social Dominance Orientation, game comprehension, and demographics. Multiple comparisons are accounted for by using a Bonferonni-corrected alpha level. Blue plots are cooperation decisions, orange plots are punishment decisions. Numbers are unstandardised coefficients. *_p_ < 0.003. DG = Dictator Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), PGG = Public Goods Game, SH = Stag Hunt Game, UG1 = Ultimatum Game (Offer), TPP1 = Third-Party Punishment Game (Steal), SPP1 = Second-Party Punishment Game (Cooperate), SHP1 = Stag Hunt Game with Punishment (Coordinate), UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP2 = Second-Party Punishment Game (Punish Cooperator), SPP3 = Second-Party Punishment Game (Punish Defector), SHP2 = Stag Hunt Game with Punishment (Punish Coordinator), SHP3 = Stag Hunt Game with Punishment (Punish Defector).

```{r indGamesPlotRWA, echo=FALSE, warning=F, message=F, fig.width=7, fig.height=4, fig.cap="(ref:indGamesPlotRWACaption)"}
readd(indGamesPlotRWA)
```

@@

```{r policyR2Plot, echo=FALSE, warning=F, message=F, fig.width=7, fig.height=6, fig.cap="(ref:policyR2PlotCaption)"}
readd(policyR2Plot)
```

@@

```{r beastImages, echo=FALSE, warning=F, message=F, fig.width=6, fig.height=7, fig.cap="(ref:beastImagesCaption)"}
readd(beastImages)
```

@@

```{r histBEAST, echo=FALSE, warning=F, message=F, warning=FALSE, message=FALSE, fig.width=7, fig.height=4, fig.cap="(ref:histBEASTCaption)"}
readd(histBEAST)
```

@@

```{r histRF, echo=FALSE, warning=F, message=F, fig.width=7, fig.height=4, fig.cap="(ref:histRFCaption)"}
readd(histRF)
```

@@

(ref:cfa1PlotCaption) _Confirmatory factor model in Study 1 using only the game decisions from previous work._ TG1 is treated as a binary endogenous variable, and paths for PGG and UG2 are constrained to 1. Note that the regression paths controlling for game comprehension are not included in this figure. Numbers are unstandardised coefficients. *_p_ < 0.05. PGG = Public Goods Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), DG = Dictator Game, UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP3 = Second-Party Punishment Game (Punish Defector).

```{r cfa1Plot, echo=FALSE, warning=F, message=F, out.width="100%", fig.cap="(ref:cfa1PlotCaption)"}
knitr::include_graphics("images/modelDrawing/cfa1.png")
```

@@

(ref:cfa2PlotCaption) _Confirmatory factor model in Study 1 with additional coordination games._ TG1 and SH are treated as binary endogenous variables, and paths for PGG and UG2 are constrained to 1. Note that the regression paths controlling for game comprehension are not included in this figure. Numbers are unstandardised coefficients. *_p_ < 0.05. PGG = Public Goods Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), DG = Dictator Game, SH = Stag Hunt Game, UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP3 = Second-Party Punishment Game (Punish Defector), SHP3 = Stag Hunt Game with Punishment (Punish Defector).

```{r cfa2Plot, echo=FALSE, warning=F, message=F, out.width="100%", fig.cap="(ref:cfa2PlotCaption)"}
knitr::include_graphics("images/modelDrawing/cfa2.png")
```

@@

@@

```{r itemTable, echo=F, warning=F, message=F}
apa_table(
  readd(itemTable), 
  booktabs = TRUE,
  caption = "(ref:itemTableCaption)"
  )
```

@@

```{r compTable, echo=F, warning=F, message=F}
apa_table(
  readd(compTable), 
  booktabs = TRUE,
  caption = "(ref:compTableCaption)",
  digits = 0
  )
```

@@

```{r semTable, echo=F, warning=F, message=F}
apa_table(
  readd(semTable), 
  booktabs = TRUE,
  caption = "(ref:semTableCaption)",
  digits = 3
  )
```

@@

```{r policy01table, echo=F, warning=F, message=F}
apa_table(
  readd(policy01table), 
  booktabs = TRUE,
  caption = "(ref:policy01tableCaption)",
  digits = 3
  )
```

@@

```{r policy02table, echo=F, warning=F, message=F}
apa_table(
  readd(policy02table), 
  booktabs = TRUE,
  caption = "(ref:policy02tableCaption)",
  digits = 3
  )
```

@@

```{r policy03table, echo=F, warning=F, message=F}
apa_table(
  readd(policy03table), 
  booktabs = TRUE,
  caption = "(ref:policy03tableCaption)",
  digits = 3
  )
```

@@

```{r policy04table, echo=F, warning=F, message=F}
apa_table(
  readd(policy04table), 
  booktabs = TRUE,
  caption = "(ref:policy04tableCaption)",
  digits = 3
  )
```

@@

```{r policy05table, echo=F, warning=F, message=F}
apa_table(
  readd(policy05table), 
  booktabs = TRUE,
  caption = "(ref:policy05tableCaption)",
  digits = 3
  )
```

@@

```{r policy06table, echo=F, warning=F, message=F}
apa_table(
  readd(policy06table), 
  booktabs = TRUE,
  caption = "(ref:policy06tableCaption)",
  digits = 3
  )
```

@@

```{r policy07table, echo=F, warning=F, message=F}
apa_table(
  readd(policy07table), 
  booktabs = TRUE,
  caption = "(ref:policy07tableCaption)",
  digits = 3
  )
```

@@

```{r policy08table, echo=F, warning=F, message=F}
apa_table(
  readd(policy08table), 
  booktabs = TRUE,
  caption = "(ref:policy08tableCaption)",
  digits = 3
  )
```

@@

```{r policy09table, echo=F, warning=F, message=F}
apa_table(
  readd(policy09table), 
  booktabs = TRUE,
  caption = "(ref:policy09tableCaption)",
  digits = 3
  )
```

@@

(ref:testRetestTableCaption) Test-retest reliability for the economic games in Peysakhovich et al. (2014) across Studies 1 and 2. Correlations are Spearman's rank correlations (all ps < 0.05). Intra-class correlations are two-way single score agreements across the two studies (all ps < 0.05).

```{r testRetestTable, echo=F, warning=F, message=F}
apa_table(
  readd(testRetestTable), 
  booktabs = TRUE,
  caption = "(ref:testRetestTableCaption)",
  digits = 2
  )
```

@@

```{r beastTable, echo=F, warning=F, message=F}
apa_table(
  readd(beastTable),
  booktabs = TRUE,
  caption = "(ref:beastTableCaption)",
  digits = 3
  )
```

```{r rfTable, echo=F, warning=F, message=F}
apa_table(
  readd(rfTable),
  booktabs = TRUE,
  caption = "(ref:rfTableCaption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable04, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable04),
  booktabs = TRUE,
  caption = "(ref:beastPolicyTable04Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable05, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable05),
  booktabs = TRUE,
  caption = "(ref:beastPolicyTable05Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable06, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable06),
  booktabs = TRUE,
  caption = "(ref:beastPolicyTable06Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable10, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable10),
  booktabs = TRUE,
  caption = "(ref:beastPolicyTable10Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable11, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable11),
  booktabs = TRUE,
  caption = "(ref:beastPolicyTable11Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable12, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable12),
  booktabs = TRUE,
  caption = "(ref:beastPolicyTable12Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable13, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable13),
  booktabs = TRUE,
  caption = "(ref:beastPolicyTable13Caption)",
  digits = 3
  )
```

@@

@@

>>>>

---
output:
  pdf_document: default
  html_document: default
---
\renewcommand{\appendixname}{\textbf{Supplementary Materials}}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{table}} \setcounter{equation}{0}

#

@@

```{r echo=F, warning=F, message=F}
loadd(cfa1)
loadd(cfa2)
loadd(cfa3)
```

@@

### Confirmatory factor analysis with method factor in Study 1

It is possible that method factors could be influencing the economic game data and generating a two-dimensional factor structure. For example, participants could simply be responding positively to all the games, regardless of their content. To test for the influence of method effects, we also included an additional method factor in the confirmatory factor model. This method factor had loadings from all game decisions, which were all constrained to 1 (i.e., a random intercept), and covariances with the cooperation and punishment factors constrained to 0. Factor loadings were relatively unchanged in this model, with all game decisions loading positively and significantly onto their respective factors (Supplementary Figure \@ref(fig:cfa3Plot)). The model continued to fit the data well (RMSEA = `r printnum(as.numeric(fitMeasures(cfa3)['rmsea']))`; SRMR = `r printnum(as.numeric(fitMeasures(cfa3)['srmr']))`; CFI = `r printnum(as.numeric(fitMeasures(cfa3)['cfi']))`). These results suggest that method factors are not driving the two-dimensional structure of gameplay.

### Structural equation model with method factor in Study 1

```{r echo=F, warning=F, message=F}
loadd(sem8)
```

We also included a method factor, as described above, in our structural equation model to check the robustness of the relationships between gameplay and political ideology to method effects. In this model, we found that SDO continued to significantly negatively predict the cooperation latent variable with a small-to-medium effect size (standardised $\beta$ = `r printnum(standardizedSolution(sem8)[30,4])`, unstandardised _b_ = `r printnum(parameterEstimates(sem8)[30,4])`, 95% confidence interval [`r printnum(parameterEstimates(sem8)[30,8])`, `r printnum(parameterEstimates(sem8)[30,9])`], _p_ `r printp(parameterEstimates(sem8)[30,7])`). SDO also continued to significantly positively predict the punishment latent variable with a small effect size ($\beta$ = `r printnum(standardizedSolution(sem8)[32,4])`, _b_ = `r printnum(parameterEstimates(sem8)[32,4], digits=3)`, 95% CI [`r printnum(parameterEstimates(sem8)[32,8], digits=3)`, `r printnum(parameterEstimates(sem8)[32,9], digits=3)`], _p_ = `r printp(parameterEstimates(sem8)[32,7])`). As in our initial model, we found no significant relationship between RWA and the punishment latent variable ($\beta$ = `r printnum(standardizedSolution(sem8)[33,4])`, _b_ = `r printnum(parameterEstimates(sem8)[33,4], digits=3)`, 95% CI [`r printnum(parameterEstimates(sem8)[33,8], digits=3)`, `r printnum(parameterEstimates(sem8)[33,9], digits=3)`], _p_ = `r printp(parameterEstimates(sem8)[33,7])`) or between RWA and the cooperation latent variable ($\beta$ = `r printnum(standardizedSolution(sem8)[31,4])`, _b_ = `r printnum(parameterEstimates(sem8)[31,4], digits=2)`, 95% CI [`r printnum(parameterEstimates(sem8)[31,8], digits=2)`, `r printnum(parameterEstimates(sem8)[31,9], digits=2)`], _p_ = `r printp(parameterEstimates(sem8)[31,7])`). These results show that method factors cannot explain the observed relationships between gameplay and political ideology.

@@

```{r samplePlot, echo=FALSE, warning=F, message=F, fig.width=10, fig.height=6, fig.cap="(ref:samplePlotCaption)", fig.pos='H', out.width="\\textwidth"}
readd(samplePlot)
```

(ref:gamesDistPlotCaption) Histograms showing distributions of decisions in the economic games in Study 1. Each game decision was normalised to vary between 0 and 1. Counts on the y-axis represent numbers of participants. DG = Dictator Game, PGG = Public Goods Game, SH = Stag Hunt Game, SHP1 = Stag Hunt Game with Punishment (Coordinate), SHP2 = Stag Hunt Game with Punishment (Punish Coordinator), SHP3 = Stag Hunt Game with Punishment (Punish Defector), SPP1 = Second-Party Punishment Game (Cooperate), SPP2 = Second-Party Punishment Game (Punish Cooperator), SPP3 = Second-Party Punishment Game (Punish Defector), TG1 = Trust Game (Give), TG2 = Trust Game (Return), TPP1 = Third-Party Punishment Game (Steal), TPP2 = Third-Party Punishment Game (Punish), UG1 = Ultimatum Game (Offer), UG2 = Ultimatum Game (Minimum Acceptable Offer).

```{r gamesDistPlot, echo=FALSE, warning=F, message=F, fig.width=5, fig.height=6, fig.cap="(ref:gamesDistPlotCaption)", fig.pos='H', out.width="\\textwidth"}
readd(gamesDistPlot)
```

@@

```{r screePlot, echo=FALSE, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="(ref:screePlotCaption)", fig.pos='H', out.width="\\textwidth"}
readd(screePlot)
```

@@

(ref:parallelPlotCaption) Scree plot from exploratory parallel analysis of economic game decisions. The parallel analysis supported a `r english(readd(parallel)$nfac)`-factor solution.

```{r parallelPlot, echo=FALSE, warning=F, message=F, fig.width=5, fig.height=5, fig.cap="(ref:parallelPlotCaption)", fig.pos='H', out.width="\\textwidth"}
knitr::include_graphics("images/parallelAnalysis.png")
```

@@

(ref:indGamesPlotSDOCaption) _Individual game decisions predicting Social Dominance Orientation in Study 1._ Lines are predictions from linear regressions, controlling for Right Wing Authoritarianism, game comprehension, and demographics. Multiple comparisons are accounted for by using a Bonferonni-corrected alpha level. Blue plots are cooperation decisions, orange plots are punishment decisions. Numbers are unstandardised coefficients. *_p_ < .003. DG = Dictator Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), PGG = Public Goods Game, SH = Stag Hunt Game, UG1 = Ultimatum Game (Offer), TPP1 = Third-Party Punishment Game (Steal), SPP1 = Second-Party Punishment Game (Cooperate), SHP1 = Stag Hunt Game with Punishment (Coordinate), UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP2 = Second-Party Punishment Game (Punish Cooperator), SPP3 = Second-Party Punishment Game (Punish Defector), SHP2 = Stag Hunt Game with Punishment (Punish Coordinator), SHP3 = Stag Hunt Game with Punishment (Punish Defector).

```{r indGamesPlotSDO, echo=FALSE, warning=F, message=F, fig.width=7, fig.height=4, fig.cap="(ref:indGamesPlotSDOCaption)", fig.pos='H', out.width="\\textwidth"}
readd(indGamesPlotSDO)
```

(ref:indGamesPlotRWACaption) _Individual game decisions predicting Right Wing Authoritarianism in Study 1._ Lines are predictions from linear regressions, controlling for Social Dominance Orientation, game comprehension, and demographics. Multiple comparisons are accounted for by using a Bonferonni-corrected alpha level. Blue plots are cooperation decisions, orange plots are punishment decisions. Numbers are unstandardised coefficients. *_p_ < .003. DG = Dictator Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), PGG = Public Goods Game, SH = Stag Hunt Game, UG1 = Ultimatum Game (Offer), TPP1 = Third-Party Punishment Game (Steal), SPP1 = Second-Party Punishment Game (Cooperate), SHP1 = Stag Hunt Game with Punishment (Coordinate), UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP2 = Second-Party Punishment Game (Punish Cooperator), SPP3 = Second-Party Punishment Game (Punish Defector), SHP2 = Stag Hunt Game with Punishment (Punish Coordinator), SHP3 = Stag Hunt Game with Punishment (Punish Defector).

```{r indGamesPlotRWA, echo=FALSE, warning=F, message=F, fig.width=7, fig.height=4, fig.cap="(ref:indGamesPlotRWACaption)", fig.pos='H', out.width="\\textwidth"}
readd(indGamesPlotRWA)
```

@@

```{r policyR2Plot, echo=FALSE, warning=F, message=F, fig.width=7, fig.height=6, fig.cap="(ref:policyR2PlotCaption)", fig.pos='H', out.width="\\textwidth"}
readd(policyR2Plot)
```

@@

```{r beastImages, echo=FALSE, warning=F, message=F, fig.width=6, fig.height=7, fig.cap="(ref:beastImagesCaption)", fig.pos='H', out.width="\\textwidth"}
readd(beastImages)
```

```{r histRF, echo=FALSE, warning=F, message=F, fig.width=7, fig.height=4, fig.cap="(ref:histRFCaption)", fig.pos='H', out.width="\\textwidth"}
readd(histRF)
```

@@

```{r histBEAST, echo=FALSE, warning=F, message=F, warning=FALSE, message=FALSE, fig.width=7, fig.height=4, fig.cap="(ref:histBEASTCaption)", fig.pos='H', out.width="\\textwidth"}
readd(histBEAST)
```

@@

(ref:cfa1PlotCaption) _Confirmatory factor model in Study 1 using only the game decisions from previous work._ TG1 is treated as a binary endogenous variable, and paths for PGG and UG2 are constrained to 1. Note that the regression paths controlling for game comprehension are not included in this figure. Numbers are unstandardised coefficients. *_p_ < .050. PGG = Public Goods Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), DG = Dictator Game, UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP3 = Second-Party Punishment Game (Punish Defector).

```{r cfa1Plot, echo=FALSE, warning=F, message=F, fig.cap="(ref:cfa1PlotCaption)", fig.pos='H', out.width="\\textwidth"}
knitr::include_graphics("images/modelDrawing/cfa1.png")
```

@@

(ref:cfa2PlotCaption) _Confirmatory factor model in Study 1 with additional coordination games._ TG1 and SH are treated as binary endogenous variables, and paths for PGG and UG2 are constrained to 1. Note that the regression paths controlling for game comprehension are not included in this figure. Numbers are unstandardised coefficients. *_p_ < .050. PGG = Public Goods Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), DG = Dictator Game, SH = Stag Hunt Game, UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP3 = Second-Party Punishment Game (Punish Defector), SHP3 = Stag Hunt Game with Punishment (Punish Defector).

```{r cfa2Plot, echo=FALSE, warning=F, message=F, fig.cap="(ref:cfa2PlotCaption)", fig.pos='H', out.width="\\textwidth"}
knitr::include_graphics("images/modelDrawing/cfa2.png")
```

@@

(ref:cfa3PlotCaption) _Confirmatory factor model in Study 1 with additional coordination games and a shared method factor._ TG1 and SH are treated as binary endogenous variables, and paths for PGG and UG2 are constrained to 1. All loadings for the method factor are constrained to 1. Note that the regression paths controlling for game comprehension are not included in this figure. Numbers are unstandardised coefficients. *_p_ < .050. PGG = Public Goods Game, TG1 = Trust Game (Give), TG2 = Trust Game (Return), DG = Dictator Game, SH = Stag Hunt Game, UG2 = Ultimatum Game (Minimum Acceptable Offer), TPP2 = Third-Party Punishment Game (Punish), SPP3 = Second-Party Punishment Game (Punish Defector), SHP3 = Stag Hunt Game with Punishment (Punish Defector).

```{r cfa3Plot, echo=FALSE, warning=F, message=F, fig.cap="(ref:cfa3PlotCaption)", fig.pos='H', out.width="\\textwidth"}
knitr::include_graphics("images/modelDrawing/cfa3.png")
```

@@

(ref:efaTableCaption) Factor loadings from an exploratory factor analysis of all items from the 16-item SDO scale (Sidanius & Pratto, 1999) and the 30-item RWA scale (Altemeyer, 1996). The factor model was fitted to a separate validation dataset of New Zealand participants (n = `r nrow(readd(dVal))`). The twelve items used in the New Zealand Attitudes and Values Study are emphasised in bold.

```{r efaTable, echo=F, warning=F, message=F}
apa_table(
  readd(efaTable), 
  booktabs = TRUE,
  longtable = TRUE,
  placement = "H",
  caption = "(ref:efaTableCaption)",
  align = c("m{2cm}", "m{11.5cm}", "m{1.5cm}", "m{1.5cm}"),
  escape = FALSE
  )
```

@@

```{r itemTable, echo=F, warning=F, message=F}
apa_table(
  readd(itemTable), 
  booktabs = TRUE,
  longtable = TRUE,
  placement = "H",
  caption = "(ref:itemTableCaption)",
  align = c("m{5cm}", "m{10cm}", "m{1.5cm}")
  )
```

@@

```{r compTable, echo=F, warning=F, message=F}
apa_table(
  readd(compTable), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:compTableCaption)",
  digits = 0
  )
```

@@

```{r semTable, echo=F, warning=F, message=F}
apa_table(
  readd(semTable) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:semTableCaption)",
  digits = 3
  )
```

@@

```{r policy01table, echo=F, warning=F, message=F}
apa_table(
  readd(policy01table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy01tableCaption)",
  digits = 3
  )
```

@@

```{r policy02table, echo=F, warning=F, message=F}
apa_table(
  readd(policy02table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy02tableCaption)",
  digits = 3
  )
```

@@

```{r policy03table, echo=F, warning=F, message=F}
apa_table(
  readd(policy03table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy03tableCaption)",
  digits = 3
  )
```

@@

```{r policy04table, echo=F, warning=F, message=F}
apa_table(
  readd(policy04table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy04tableCaption)",
  digits = 3
  )
```

@@

```{r policy05table, echo=F, warning=F, message=F}
apa_table(
  readd(policy05table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy05tableCaption)",
  digits = 3
  )
```

@@

```{r policy06table, echo=F, warning=F, message=F}
apa_table(
  readd(policy06table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy06tableCaption)",
  digits = 3
  )
```

@@

```{r policy07table, echo=F, warning=F, message=F}
apa_table(
  readd(policy07table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy07tableCaption)",
  digits = 3
  )
```

@@

```{r policy08table, echo=F, warning=F, message=F}
apa_table(
  readd(policy08table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy08tableCaption)",
  digits = 3
  )
```

@@

```{r policy09table, echo=F, warning=F, message=F}
apa_table(
  readd(policy09table) %>% mutate(p = str_sub(as.character(format(round(p, 3), nsmall = 2)), 2, -1)), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:policy09tableCaption)",
  digits = 3
  )
```

@@

(ref:testRetestTableCaption) Test-retest reliability for the economic games in Peysakhovich et al. (2014) across Studies 1 and 2. Correlations are Spearman's rank correlations (all _p_ < .050). Intra-class correlations are two-way single score agreements across the two studies (all _p_ < .050).

```{r testRetestTable, echo=F, warning=F, message=F}
apa_table(
  readd(testRetestTable), 
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:testRetestTableCaption)",
  digits = 2
  )
```

```{r rfTable, echo=F, warning=F, message=F}
apa_table(
  readd(rfTable),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:rfTableCaption)",
  digits = 3
  )
```

@@

```{r beastTable, echo=F, warning=F, message=F}
apa_table(
  readd(beastTable),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:beastTableCaption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable04, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable04),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:beastPolicyTable04Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable05, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable05),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:beastPolicyTable05Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable06, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable06),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:beastPolicyTable06Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable10, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable10),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:beastPolicyTable10Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable11, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable11),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:beastPolicyTable11Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable12, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable12),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:beastPolicyTable12Caption)",
  digits = 3
  )
```

@@

```{r beastPolicyTable13, echo=F, warning=F, message=F}
apa_table(
  readd(beastPolicyTable13),
  booktabs = TRUE,
  placement = "H",
  caption = "(ref:beastPolicyTable13Caption)",
  digits = 3
  )
```

@@

Altemeyer, B. (1996). _The authoritarian specter_. London: Harvard University Press.

@@

Sidanius, J., & Pratto, F. (1999). _Social dominance: An intergroup theory of social hierarchy and oppression_. Cambridge: Cambridge University Press.
